---
title: "Group 9 Amber India Restaurants Project"
author: "Aashna Rungta, Eshna Reza, Sandhya N, Sony Kumari, Sneha Batchu"

output:
  html_document: default
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}

# Clear the working space
    rm(list = ls())
 
# Load the packages (all must have been installed)  
    library(doBy)
    library(dplyr)
    library(foreign)
    library(ggplot2)
    library(knitr)
    library(lmtest)
    library(readstata13)
    library(sandwich)
    library(stargazer)
    library(AER)
    library(gdata)
    library(wooldridge)
    library(tidyr)
    library(openintro)
    library(alabama)

```


## Part 1:  

Using the two-phase method, we need to first find the initial value for the optimization with dummy variables:

```{r two_phase, echo=FALSE, message=F, warning=FALSE, comment="", results = "hide"}
func=function(x) x[4]^2 + x[5]^2 #dummy variables for two phase

p0=c(0, 0, 0, 5001, 5001) #choosing dummy values to satisfy all the inequalities

#Equality Constraints
g1=function(x) {
  h= 0
  h[1]= 1490 - 40*x[2] - 120*x[3] #coupon redemption equation
  return (h)}

g2=function(x) {
  h=0
  h[1]= -5000 + 1200*x[1] + 200*x[2] + x[4] #young people
  h[2]= -5000 + 500*x[1] + 200*x[2] + 200 *x[3] + x[5] #old people 
  h[3]= 4000 - 300*x[1] - 150*x[2] - 100 * x[3] #ad costs for 1 year
  h[4]= 1000 - 90*x[1] - 30*x[2] - 40*x[3] #planning costs
  h[5]= 5 - x[1] #max TV ads
  return (h) }

y= constrOptim.nl(p0,func,heq=g1,hin=g2) 

#initial values input  for the actual optimization in next code chunk
p0=y$par[1:3]
print(p0) 

```

The initial values we get are `r p0`, which will be the initial values for the actual optimization:

```{r exposures optimization, echo=FALSE, message=F, warning=FALSE, comment="", results = "hide"}

func=function(x) -(1300 * x[1] +  600 * x[2] +  500 * x[3])

p1= c(3.024600, 8.886762, 9.454413)

g1=function(x){
  h=0
  h[1]= 40*x[2] + 120*x[3] - 1490
  return (h)}

g2=function(x){
  h=0
h[1]=  1200*x[1] +  200*x[2] - 5000 #young people
h[2]=  500*x[1] + 200*x[2] + 200 *x[3] + 5000 #old people 
h[3]=  - 300*x[1] - 150*x[2] - 100 * x[3] + 4000 #ad costs for 1 year
h[4]=  - 90*x[1] - 30*x[2] - 40*x[3] + 1000 #planning costs
h[5]= - x[1] + 5 #max tv ads
# h[6]= x[2] + x[6]
# h[7]= x[3] + x[7]
# h[8]= x[1] + x[205]
return (h)}

y=constrOptim.nl(par=p1,fn=func,heq=g1,hin=g2)

print(paste0(y$par," is the proportion of tv ads"))
print(paste0("$",-y$value*1000," is the approximation of profit as per Vijay's estimate."))
```
The optimal values for the TV, Magazine and Newspaper Ads are respectively: `r y$par`.   

Also, the total exposures is `r -y$value*1000`

We also found another way to get the same optimal values for the cost and budget equations using matrices:
```{r part 1 approach 2, echo=FALSE}

Cost= matrix(c(300000,150000,100000,90000,30000,40000,0,40000,120000),byrow = TRUE,nrow=3, ncol=3)
Budget=matrix(c(4000000,1000000,1490000),byrow = TRUE)
solve(Cost,Budget)

Exposure= matrix(c(1200000,200000,0,500000,200000,200000,1300000,600000,500000),byrow = TRUE,nrow=3, ncol=3)
Min_exposure=matrix(c(5000000,5000000,1000000),byrow = TRUE)

```


## Part 2:  
```{r part2, echo=FALSE}

tv=2.318182
m=17.681818
n=6.522727

#Vijay's Approximation of Profit function
exposures = 1300000*tv +  600000*m +  500000*n

#BayCreative's Approach to Profit Calculation
tv_first = -0.1*(tv^2)+ 1.13*tv - 0.04 #First time TV visits
m_first  = -0.002*(m^2) + 0.124*m + 0.14 #First time magazine impressions
n_first  = -0.0321*(n^2) + 0.706*n - 0.09 #First time newspaper impressions

first_visit=(tv_first+m_first+n_first)*1000000
profit_per_customer=first_visit*5

ad_cost = 300000*tv + 150000*m + 100000*n  
planning_cost =  90000*tv + 30000*m + 40000*n

net_profit=profit_per_customer - ad_cost - planning_cost

print(paste0("$",net_profit," is the Net Profit based on the detailed calculations"))
print(paste0("$",exposures, " is Vijay's approximation of Profit based on exposure to ads"))

```



## Part 3:  

$E(P) = \int_{200}^{q} (12*25*X - 75*q)*f(X)\,dX + \int_{q}^{500} (12*25*q - 75*q)*f(X)\,dX$

$E(P) = \int_{200}^{q} (300*X - 75*q)*\dfrac{1}{300}\,dX + \int_{q}^{500} (225*q)*\dfrac{1}{300}\,dX$

$E(P) = \int_{200}^{q} (X - \dfrac{q}{4})\,dX + \int_{q}^{500} (q*\dfrac{3}{4})\,dX$

Solving the integral, we get, $E(P) = \dfrac{-1}{2} * q^2 + 425*q - \dfrac{1}{2}*200^2$  

 To get maximum profit, $\dfrac{d E(P)}{dX} = 0$  

$\dfrac{dE(P)}{dq} = -q + 425 = 0$   

$q = 425$    

Using the above quantity (425 gallons/week), we get the following optimal profit value:  

$p = 12*25*X - 75*q$

$p = 12 * 25 * [\dfrac{200+425}{2} \int_{200}^{425}\, f(X) dX + 425 * \int_{425}^{500}\,f(X)dX] - 75*425$  

$p = 300 * [312.5 * (\dfrac{425}{300} - \dfrac{200}{300}) + 425 * (\dfrac{500}{300} - \dfrac{425}{300})] - 31875$

$p = 102187.5 - 31875 =\$70312.5$

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
